### 2013-09-13 tab_mr_arfi_volumes.tex
updated formatting in table and figs

\begin{table}
\centering
\caption{Comparison of Central Gland / Zone and Total Prostate Volumes in MR T2WI and ARFI Imaging}
\begin{tabular}{|l|l|l|l|l|} \hline
{\bf Study Subject} & {\bf MR Central Gland} & {\bf MR Total} & {\bf ARFI Central Zone} & {\bf ARFI Total} \\ 
& {\bf Volume (mm$^3$)} & {\bf Volume (mm$^3$)} & {\bf Volume (mm$^3$)} & {\bf Volume (mm$^3$)} \\ \hline
P86 & 12738.12 & 24567.06 & 14296. & 40031. \\
P79 & 14263.86 & 28514.79 & 8370 & 33978 \\
P78 & 23471.81 & 32484.36 & 13290.47 & 37420 \\
P77 & 17317.03 & 32492.83 & 10829.7 & 31819 \\
P75 & 57561.69 & 70950.98 & 30369 & 73684.64 \\
P74 & 12010.3 & 27841.21 & 15679 & 43298.34 \\
P72 & 8824.44 & 19587.02 & 11776.44 & 28545.79 \\
P71 & 10969.65 & 21276.98 & 16020.73 & 31424.61 \\
P70 & 13633.36 & 20749.91 & 19282 & 36876.3\\
P69 & 23580.12 & 36112.58 & 33500 & 70654 \\
P67 & 16569.17 & 27332.39 & 25219 & 34656.2 \\
P61 & 25381.36 & 49213.93 & 18137 & 54044.3 \\
P59 & 9247.34 & 26360.37 & 6144 & 35137 \\
P58 & 14787.88 & 23361.47 & 19654.6 & 35211 \\
P57 & 17872.15 & 35371.12 & 10153 & 38028.47 \\
P56 & 33315.41 & 48495.39 & 39351 & 66425 \\ \hline
\end{tabular}
\label{tab:mr_arfi_volumes}
\end{table}

>>>>

\begin{table}
\centering
\caption{Comparison of Central Gland / Zone and Total Prostate Volumes in MR T2WI and ARFI Imaging}
\begin{tabular}{|l|l|l|l|l|} \hline
{\bf Study Subject} & {\bf MR Central Gland} & {\bf MR Total} & {\bf ARFI Central Zone} & {\bf ARFI Total} \\ 
& {\bf Volume (cm$^3$)} & {\bf Volume (cm$^3$)} & {\bf Volume (cm$^3$)} & {\bf Volume (cm$^3$)} \\ \hline
\input{data/vol_data}
\hline
\end{tabular}
\label{tab:mr_arfi_volumes}
\end{table}
